Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-08 tex/sections/intro.tex
Add a notice for Chapter 2
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance System
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the blockchain.
Each minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system. A block is
approved if it takes approval votes from at least \(2/3\) of the total stake of its validator committee.

>>>>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance System
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the blockchain.
Each minted block is required to get approved by its corresponding validator committee. Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system. A block is
approved if it takes approval votes from at least \(2/3\) of the total stake of its validator committee.
